Tree-structured neural networks revisited

### 2016-03-05 writing/hard_stack_paper/paper.tex
Incremental paper update.

\begin{figure}[t]
\begin{subfigure}[t]{0.9\columnwidth}
\vspace{14em}
\todo{[SB] Figure showing why trees can't be batched (modeled after slides).}

\caption{\label{fig:batching:bad}Trees are hard to batch.}
\end{subfigure}

\vspace{2em}

\begin{subfigure}[t]{0.9\columnwidth}
\vspace{14em}
\todo{[SB] Figure showing a batch of sequences (modeled after slides).}

\caption{\label{fig:batching:good}Sequences are easy to batch.}
\end{subfigure}
\caption{An illustration of a conventionally-implemented TreeRNN model (a) and our equivalent model (b).}
\end{figure}

@@

\paragraph{Accumulating results sequentially} (After Rocktäschel, Wang and Jiang)

\paragraph{Accumulating results using a second tree layer}

@@

                        & 1.4m               &   92.3   &   89.1      \\
\midrule
\multicolumn{4}{c}{New results}\\
\midrule
\result{150d LSTM RNN      }     & ?                  &   ?      &   ?       \\
\result{150d TB TreeLSTM}   
                        & ?                  &   ?      &   ?       \\
\result{150d TB TreeLSTM w/ tracking    }
                        & ?                  &   ?      &   ?       \\
\result{150d TB TreeLSTM w/ tracking, sequence-based attn.   }     
                        & ?                  &   ?      &   ?       \\
\result{150d TB TreeLSTM w/ tracking, tree-based attn. }           
                        & ?                  &   ?      &   \textbf{?}\\
    \bottomrule
  \end{tabular}
  \protect\caption{\protect\label{tab:results}Results on SNLI 3-way inference classification. All reported figures are percent accuracy. \result{[JG]Add seconds-per-step *if* we get a reasonably well-optimized model in time.}} 
\end{table*}

@@

\paragraph{Patterns in the examples that the tree model got right that the LSTM didn't}

\paragraph{Induced alignments}

@@

In future work, we aim to incorporate a parser into our model, allowing it to simultaneously learn to parse sentences (using a conventional parsing objective function) and to use those parses to learn semantic representations for those sentences (using a classification objective function, as in this work). Implementing such a model on top of our proposed stack-based design would learn a model that could productively share representations between the two tasks. Implementing such a model on top of a differentiable version of our stack-based design (possibly following \citealt{grefenstette2015learning} \todo{[SB] Cite FAIR stack paper.}) would further make it possible for the model to learn to parse using guidance from the semantic representation objective, essentially allowing  learn to produce parses that are, in aggregate, better suited to supporting semantic interpretation than those supplied in the training data.

>>>>

\input{batching_fig.tex}

@@

\todo{[RG,AR] Accumulating results sequentially  (After Rocktäschel, Wang and Jiang)}

\todo{[RG,SB] Accumulating results using a second tree layer}

@@

                        & 1.4m               &   92.3   &   89.1      \\
\midrule
\multicolumn{4}{c}{New results}\\
\midrule
\result{150d LSTM RNN      }     & ?                  &   ?      &   81?       \\
\result{150d TB TreeLSTM}   
                        & ?                  &   ?      &   81?       \\
\result{150d TB TreeLSTM w/ tracking    }
                        & ?                  &   ?      &   83?       \\
\result{150d TB TreeLSTM w/ tracking, sequence-based attn.   }     
                        & ?                  &   ?      &   85+?       \\
\result{150d TB TreeLSTM w/ tracking, tree-based attn. }           
                        & ?                  &   ?      &   \textbf{?}\\
    \bottomrule
  \end{tabular}
  \protect\caption{\protect\label{tab:results}Results on SNLI 3-way inference classification. All reported figures are percent accuracy. \result{[JG]Add seconds-per-step *if* we get a reasonably well-optimized model in time.}} 
\end{table*}

@@

\result{Patterns in the examples that the tree model got right that the LSTM didn't}

\result{Induced alignments}

@@

In future work, we aim to incorporate a parser into our model, allowing it to simultaneously learn to parse sentences (using a conventional parsing objective function) and to use those parses to learn semantic representations for those sentences (using a classification objective function, as in this work). Implementing such a model on top of our proposed stack-based design would learn a model that could productively share representations between the two tasks. Implementing such a model on top of a differentiable version of our stack-based design (possibly following \citealt{grefenstette2015learning,joulin2015inferring}) would further make it possible for the model to learn to parse using guidance from the semantic representation objective, essentially allowing  learn to produce parses that are, in aggregate, better suited to supporting semantic interpretation than those supplied in the training data.
